Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-08-13 analysis/Manuscript/Paper_RFigures.Rmd
paper review updates

```{r libraries, include = FALSE}
library('tidyverse')
library('reshape2')
library('patchwork')
library('RColorBrewer')
#library('maps')
#library('mapproj')
library('arrow')
library('readxl')
library('zoo')
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
```

@@

#define paths
Plots <-file.path('analysis','Manuscript','Plots') 
inputs <- file.path("analysis","Manuscript")
inputs2 <- file.path('input','RFF','lookup_tables')
inputs3 <- file.path("input")
Inputs_socio <- file.path('input','RFF','rft_inputs')

#Read in RFF-SP data
# Pre-processed in /code/1_build_inputs_for_momm_rft.R
rffsp <- read_parquet(file.path(getwd(),Inputs_socio, 'rffsp_pop_gdp_all_trials.parquet'))

@@

#plot global MMM with uncertainty bounds (from CRF uncertainty)
global_limits<- globalResults2.5long %>%
  filter(Model %in% c('MMM - Mean AQS')) %>%
  mutate(Model = 'lower') %>%
  rbind(globalResults97.5long) %>%
  filter(Model %in% c('lower','MMM - Mean AQS')) %>%
  mutate(Model = case_when( Model == 'MMM - Mean AQS' ~ 'upper',TRUE ~ Model)) %>%
  #spread(Model,value) %>%
  #rename(upper = `MMM - Mean AQS`) %>%
  rbind(globalResultslong) %>%
  filter(Model %in% c('lower','upper','MMM - Mean AQS')) %>%
  spread(Model,value)
p1_bounds <- global_limits %>%
    ggplot(aes(x=Model.years,y=`MMM - Mean AQS`,ymin=lower, ymax=upper,fill='MMM &\nCRF Distribution'))+
        geom_point()+
        geom_line()+
        geom_ribbon(alpha=0.5) +
        scale_linetype_manual(values="solid","longdash","longdash")+
        scale_colour_manual('',values="black")+
        scale_fill_manual("",values="gray50")+
        scale_size_manual(values=c(rep(1,5),1.5,1))+
        xlab("Year")+ylab("Deaths")+
        ggtitle('Global Annual Respiratory-Related Ozone Attributable Mortality')+
        theme_minimal()+
        scale_x_continuous(breaks=seq(2020,2100,10))+
        scale_y_continuous(limits=c(0,18000), labels=scales::comma)+
        theme(legend.position = c(0.15, 0.15), legend.text = element_text(size=16))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16),
              axis.text.x=element_text(angle=45,hjust=1, vjust=1))
p1_bounds
ggsave(plot = p1_bounds, filename = 
         file.path(Plots,'Plots/Timeseries_O3Mort_CRFbounds.png'),width = 9,height = 5)

@@

#map of country mortality results
MODEL = 'GFDL'

Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
input <- file.path(getwd(),'input','BenMAP')
countryResults <- read.csv(paste0(input,"/Country Results Summary by Model & Year.csv"))

@@

Plots <- file.path( 'analysis','Manuscript','Plots')
input <- file.path('../..','input')

@@

Plots <- file.path('../..','analysis','Manuscript','Plots')
inputs <- file.path('../..','analysis','Manuscript','BenMAP','Outputs')
countryresults <-
   read_csv(file.path(inputs,"npd_country_damage_transformation_woutCessation.csv"),
           col_types = cols())

globalresults <-
  read_csv(file.path(inputs, "npd_global_damage_transformation_woutCessation.csv"),
           col_types = cols())

@@

Results <- file.path('Results')
globalresults <-
  read_csv(file.path(inputs,"npd_global_damage_transformation_woutCessation.csv"),
           col_types = cols())
Results2 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())
nox_results1 <- file.path(rft_inputs,'npd_global_means_NOx_1_MMM.csv')
nox_results1 <- read_csv(nox_results1, col_types = cols())%>%
  mutate(NOx = '1')
nox_results5 <- file.path(rft_inputs, 'npd_global_means_NOx_0.5_MMM.csv')
nox_results5 <- read_csv(nox_results5, col_types = cols())%>%
  mutate(NOx = '0.5')
nox_results15 <- file.path(rft_inputs, 'npd_global_means_NOx_1.5_MMM.csv')
nox_results15 <- read_csv(nox_results15, col_types = cols()) %>%
  mutate(NOx = '1.5')
nox_total_results <- rbind(nox_results1,nox_results5,nox_results15)

>>>>

```{r libraries, include = FALSE}
library('tidyverse')
library('reshape2')
require('patchwork')
require('RColorBrewer')
#library('maps')
#library('mapproj')
library('arrow')
require('readxl')
library('zoo')
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
```

@@

#define paths
Plots <-file.path('../..','analysis','Manuscript','Plots') 
inputs <- file.path('../..',"analysis","Manuscript")
inputs2 <- file.path('../..','input','RFF','lookup_tables')
inputs3 <- file.path('../..',"input")
Inputs_socio <- file.path('../..','input','RFF','rft_inputs')

#Read in RFF-SP data
# Pre-processed in /code/1_build_inputs_for_momm_rft.R
rffsp <- read_parquet(file.path(Inputs_socio, 'rffsp_pop_gdp_all_trials.parquet'))

@@

#plot global MMM with uncertainty bounds (from CRF uncertainty)
global_limits<- globalResults2.5long %>%
  filter(Model %in% c('MMM - Mean AQS')) %>%
  mutate(Model = 'lower') %>%
  rbind(globalResults97.5long) %>%
  filter(Model %in% c('lower','MMM - Mean AQS')) %>%
  mutate(Model = case_when( Model == 'MMM - Mean AQS' ~ 'upper',TRUE ~ Model)) %>%
  #spread(Model,value) %>%
  #rename(upper = `MMM - Mean AQS`) %>%
  rbind(globalResultslong) %>%
  filter(Model %in% c('lower','upper','MMM - Mean AQS')) %>%
  spread(Model,value)
p1_bounds <- global_limits %>%
    ggplot(aes(x=Model.years,y=`MMM - Mean AQS`,ymin=lower, ymax=upper,fill='MMM &\nCRF Distribution'))+
        geom_point()+
        geom_line()+
        geom_ribbon(alpha=0.5) +
        scale_linetype_manual(values="solid","longdash","longdash")+
        scale_colour_manual('',values="black")+
        scale_fill_manual("",values="gray50")+
        scale_size_manual(values=c(rep(1,5),1.5,1))+
        xlab("Year")+ylab("Deaths")+
        ggtitle('Global Annual Respiratory-Related Ozone Attributable Mortality')+
        theme_minimal()+
        scale_x_continuous(breaks=seq(2020,2100,10))+
        scale_y_continuous(limits=c(0,18000), labels=scales::comma)+
        theme(legend.position = c(0.15, 0.15), legend.text = element_text(size=16))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16),
              axis.text.x=element_text(angle=45,hjust=1, vjust=1))
p1_bounds
ggsave(plot = p1_bounds, filename = 
         file.path(Plots,'Fig2a.png'),width = 9,height = 5)

@@

Plots <- file.path('../..','analysis','Manuscript','Plots')
input <- file.path('../..','input','BenMAP')
countryResults <- read.csv(paste0(input,"/Country Results Summary by Model & Year.csv"))

@@

Plots <- file.path('../..','analysis','Manuscript','Plots')
input <- file.path('../..','input')

@@

Plots <- file.path('../..','analysis','Manuscript','Plots')
inputs <- file.path('../..','analysis','Manuscript','BenMAP','Outputs')
countryresults <-
   read_csv(file.path(inputs,"npd_country_damage_transformation_woutCessation_vsl10.csv"),
           col_types = cols())

globalresults <-
  read_csv(file.path(inputs, "npd_global_damage_transformation_woutCessation_vsl10.csv"),
           col_types = cols())

@@

Results <- file.path('Results')
# CRF results - from BenMAP valuation script
globalresults <-
  read_csv(file.path(inputs,"npd_global_damage_transformation_woutCessation_vsl10.csv"),
           col_types = cols())

#Socioeconomic results - from RFT code
Results2 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())

#NOx sensitivity results- from RFT code
nox_results1 <- file.path(rft_inputs,'npd_global_means_vsl10_NOx_1_MMM.csv')
nox_results1 <- read_csv(nox_results1, col_types = cols())%>%
  mutate(NOx = '1')
nox_results5 <- file.path(rft_inputs, 'npd_global_means_vsl10_NOx_0.5_MMM.csv')
nox_results5 <- read_csv(nox_results5, col_types = cols())%>%
  mutate(NOx = '0.5')
nox_results15 <- file.path(rft_inputs, 'npd_global_means_vsl10_NOx_1.5_MMM.csv')
nox_results15 <- read_csv(nox_results15, col_types = cols()) %>%
  mutate(NOx = '1.5')
nox_total_results <- rbind(nox_results1,nox_results5,nox_results15)
